Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-09-24 paper/paper.tex
title corrected
pros and cons of Jupyter and Jupyterhub formulated

\title{Experiences in teaching with Jupyter with nbgrader}
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\section{Section title}
\label{sec:1}

\subsection{Subsection title}
\label{sec:2}

@@

\section{Jupyter and Jupyterhub}

pros and cons of using the Jupyter notebook
\begin{itemize}
 \item notebook allows to guide students through a problem set
 \item problems related to out-of-order execution
 \item \textit{but} students might think that programming in Python
       necessarily implies working with a Jupyter notebook,
       they should know about IDEs (spyder, \dots) and
       editors (vim, \dots)
\end{itemize}

pros and cons of using Jupyterhub
\begin{itemize}
 \item easily accessible interface to problem sets
 \item no need to install Python on local computer
 \item consistent working environment for all students
 \item \textit{but} may be beginners should gather experience with Python
       on their own computer
\end{itemize}

>>>>

\title{Experiences in teaching with Jupyter, Jupyterhub, and nbgrader}
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

@@

\section{Jupyter and Jupyterhub}
\label{sec:jupyter_jupyterhub}

A Jupyter notebook consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown, possibly
including formulas as well as figures. This structure facilitates to guide
students through a problem set. Usually, the code in a notebook is intended to
be executed in a linear fashion even though this is not imposed by the
notebook. In fact, the notebook should invite students to experiment which
implies the opening of new cells and the execution of code written by the
student. In this process, out-of-order execution naturally occurs and can have
side effects which tend to confuse students. While the order of execution of
individual cells can be inferred by the sequence number attributed to a cell
once it has been executed, in particular beginners are not aware of the
problems that out-of-order execution can entail.

Using the Jupyter notebook for exercises is interesting because students can
easily experiment with code. At the same time one should be aware that students
might think that this is the standard way of programming in Python. While it is
indeed possible to develop pieces of a more complex program in the Jupyter 
notebook and later combine these pieces, this is not the standard approach for
complex programming tasks. Therefore, students should also be acquainted with
the IDEs like Spyder distributed with the Anaconda distribution or the use of
editors like vim or others which can be configures to support programming in
Python.

Jupyterhub as a centrally provided resource to run a Jupyter notebook from a
remote computer makes problem sets or more generally teaching material easily
accessible without the need for a local Python installation. Furthermore, this
approach ensures a consistent working environment for all students. However,
it might be an important experience for students that all work which they
are doing could in fact be done on their own computer instead of using some
remote service where the underlying machinery is completely hidden.
